---
title: "Project 1 - Hello _R_ You There"
author: "Ryan Cheung"
date: "Due Fed 3rd"
output: 
  html_document: 
    fig_width: 6
    fig_height: 6
    highlight: kate
    theme: cosmo
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1
Based on the help file, how many rows and how many columns does the datasaurus_dozen file have?  
What are the variables included in the data frame?  
  
|__Rows__|__Columns__|__Varibles List__|
|:------------|:------------|:------------|
|1846|3|dataset, x, y|  

### Exercise 2  

First, let's plot the data in the dino dataset:  
  
>Ryan's Notes: Filter for data matching "dino" using dataset datasaurus_dozen, marked with pipe operator.   
Visualize using ggplot(data,mapping = aes_thetics(x = column_from_data,y = column_from_data) + define_plot_point_shape)  

```{r plot-dino}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next, calculate the correlation between `x` and `y` in this dataset, then store and display as varible "dino_cor":

```{r cor-dino}
dino_cor <- dino_data %>%
  summarize(r = cor(x, y))
dino_cor
```

### Exercise 3

Now, let's plot the 'star' data.

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And also calculate the correlation coefficient between x and y in the 'star' data, then store and display as variable "star_cor".
 
```{r cor-star}
star_cor <- star_data %>%
  summarize(r = cor(x, y))
star_cor
```

The correlation values from dino_data (-0.06447185) and star_data (-0.0629611) are very similar, around 2.343% difference.

```{r simple-comparison-dino-star}
dino_star_diff <- (-0.06447185--0.0629611)/-0.06447185
dino_star_diff
```

### Exercise 4

Next, let's plot the 'circle' data.

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And also calculate the correlation coefficient between x and y in the 'circle' data, then store and display as variable "circle_cor".
 
```{r cor-circle}
circle_cor <- circle_data %>%
  summarize(r = cor(x, y))
circle_cor
```

The correlation values from dino_data (-0.06447185) and circle_data (-0.06834336) are also similar, but not as similar as the dino/star data; around 6.005% difference.

```{r simple-comparison-dino-circle}
dino_circle_diff <- (-0.06447185--0.06834336)/-0.06447185
dino_circle_diff
```

### Exercise 5

Finally, let’s plot all datasets at once and calculate their summary correlation coefficients. In order to do this we will make use of _facetting_.

```{r plot-all, fig.height=8, fig.width=8}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")
```
  
And we can use the group_by function to generate and display all the summary correlation coefficients.

```{r}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)
```

