---
title: "Project 1 - Hello _R_ You There"
author: "Ryan Cheung"
date: "Due Fed 3rd"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

|__Rows__|__Columns__|__Varibles List__|
|:------------|:------------|:------------|
|1846|3|dataset, x, y|

### Exercise 2

First, let's plot the data in the dino dataset:  
  
Filter for data matching "dino" using dataset datasaurus_dozen, marked with pipe operator.  
Visualize using ggplot(data,mapping = aes_thetics(x = column_from_data,y = column_from_data) + define_plot_point_shape)  

```{r plot-dino, fig.height=6, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next, calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Now, let's plot the 'star' data.

```{r plot-star, fig.height=6, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And also calculate the correlation coefficient between x and y in the 'star' data.
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}


```

```{r}


```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
